\HeaderA{aggr}{Aggregations for missing/imputed values}{aggr}
\aliasA{plot.aggr}{aggr}{plot.aggr}
\aliasA{TKRaggr}{aggr}{TKRaggr}
\keyword{hplot}{aggr}
%
\begin{Description}\relax
Calculate or plot the amount of missing/imputed values
in each variable and the amount of missing/imputed values
in certain combinations of variables.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
aggr(x, delimiter = NULL, plot = TRUE, ...)

## S3 method for class 'aggr'
plot(x, col = c("skyblue","red","orange"), bars = TRUE,
    numbers = FALSE, prop = TRUE, combined = FALSE, varheight = FALSE,
    only.miss = FALSE, border = par("fg"), sortVars = FALSE,
    sortCombs = TRUE, ylabs = NULL, axes = TRUE, labels = axes,
    cex.lab = 1.2, cex.axis = par("cex"), cex.numbers = par("cex"),
    gap = 4, ...)

TKRaggr(x, ..., delimiter = NULL, hscale = NULL, vscale = NULL,
    TKRpar = list())
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] a vector, matrix or \code{data.frame}.
\item[\code{delimiter}] a character-vector to distinguish between variables
and imputation-indices for imputed variables (therefore, \code{x} needs
to have \code{\LinkA{colnames}{colnames}}). If given, it is used to determine the corresponding
imputation-index for any imputed variable (a logical-vector indicating
which values of the variable have been imputed). If such imputation-indices
are found, they are used for highlighting and the colors are adjusted 
according to the given colors for imputed variables (see \code{col}).
\item[\code{plot}] a logical indicating whether the results should be plotted 
(the default is \code{TRUE}).
\item[\code{col}] a vector of length three giving the colors to be used for 
observed, missing and imputed data. If only one color is supplied, it is 
used for missing and imputed data and observed data is transparent. If 
only two colors are supplied, the first one is used for observed data and
the second color is used for missing and imputed data.
\item[\code{bars}] a logical indicating whether a small barplot for the 
frequencies of the different combinations should be drawn.
\item[\code{numbers}] a logical indicating whether the proportion or frequencies 
of the different combinations should be represented by numbers.
\item[\code{prop}] a logical indicating whether the proportion of missing/imputed values 
and combinations should be used rather than the total amount.
\item[\code{combined}] a logical indicating whether the two plots should be 
combined.  If \code{FALSE}, a separate barplot on the left hand side shows 
the amount of missing/imputed values in each variable.  If \code{TRUE}, a small 
version of this barplot is drawn on top of the plot for the combinations of 
missing/imputed and non-missing values.  See ``Details'' for more information.
\item[\code{varheight}] a logical indicating whether the cell heights are given by 
the frequencies of occurrence of the corresponding combinations.
\item[\code{only.miss}] a logical indicating whether the small barplot for the 
frequencies of the combinations should only be drawn for combinations 
including missing/imputed values (if \code{bars} is \code{TRUE}).  This is useful 
if most observations are complete, in which case the corresponding bar would 
dominate the barplot such that the remaining bars are too compressed.  The 
proportion or frequency of complete observations (as determined by 
\code{prop}) is then represented by a number instead of a bar.
\item[\code{border}] the color to be used for the border of the bars and 
rectangles.  Use \code{border=NA} to omit borders.
\item[\code{sortVars}] a logical indicating whether the variables should be 
sorted by the number of missing/imputed values.
\item[\code{sortCombs}] a logical indicating whether the combinations should be 
sorted by the frequency of occurrence.
\item[\code{ylabs}] if \code{combined} is \code{TRUE}, a character string giving the 
y-axis label of the combined plot, otherwise a character vector of 
length two giving the y-axis labels for the two plots.
\item[\code{axes}] a logical indicating whether axes should be drawn.
\item[\code{labels}] either a logical indicating whether labels should be 
plotted on the x-axis, or a character vector giving the labels.
\item[\code{cex.lab}] the character expansion factor to be used for the axis labels.
\item[\code{cex.axis}] the character expansion factor to be used for the axis 
annotation.
\item[\code{cex.numbers}] the character expansion factor to be used for the 
proportion or frequencies of the different combinations
\item[\code{gap}] if \code{combined} is \code{FALSE}, a numeric value giving the 
distance between the two plots in margin lines.
\item[\code{...}] for \code{aggr} and \code{TKRaggr}, further arguments and 
graphical parameters to be passed to \code{\LinkA{plot.aggr}{plot.aggr}}.  For 
\code{plot.aggr}, further graphical parameters to be passed down.  
\code{par("oma")} will be set appropriately unless supplied (see 
\code{\LinkA{par}{par}}).
\item[\code{hscale}] horizontal scale factor for plot to be embedded in a 
\emph{Tcl/Tk} window (see `Details').  The default value 
depends on the number of variables.
\item[\code{vscale}] vertical scale factor for the plot to be embedded in a 
\emph{Tcl/Tk} window (see `Details').  The default value 
depends on the number of combinations.
\item[\code{TKRpar}] a list of graphical parameters to be set for the plot 
to be embedded in a \emph{Tcl/Tk} window (see `Details' and 
\code{\LinkA{par}{par}}).
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
Often it is of interest how many missing/imputed values are contained in each 
variable.  Even more interesting, there may be certain combinations of 
variables with a high number of missing/imputed values.

If \code{combined} is \code{FALSE}, two separate plots are drawn for the 
missing/imputed values in each variable and the combinations of missing/imputed and 
non-missing values. The barplot on the left hand side shows the amount of 
missing/imputed values in each variable.  In the \emph{aggregation plot} on the right 
hand side, all existing combinations of missing/imputed and non-missing values in 
the observations are visualized.  Available, missing and imputed data are color
coded as given by \code{col}.  Additionally, there are two possibilities to 
represent the frequencies of occurrence of the different combinations.  The 
first option is to visualize the proportions or frequencies by a small bar 
plot and/or numbers.  The second option is to let the cell heights be given 
by the frequencies of the corresponding combinations. Furthermore, variables 
may be sorted by the number of missing/imputed values and combinations by the 
frequency of occurrence to give more power to finding the structure of 
missing/imputed values.

If \code{combined} is \code{TRUE}, a small version of the barplot showing 
the amount of missing/imputed values in each variable is drawn on top of the 
aggregation plot.

The graphical parameter \code{oma} will be set unless supplied as an 
argument.

\code{TKRaggr} behaves like \code{plot.aggr}, but uses 
\code{\LinkA{tkrplot}{tkrplot}} to embed the plot in a \emph{Tcl/Tk} 
window.  This is useful if the number of variables and/or combinations 
is large, because scrollbars allow to move from one part of the plot 
to another.
\end{Details}
%
\begin{Value}
for \code{aggr}, a list of class \code{"aggr"} containing the following 
components:
\begin{ldescription}
\item[\code{x}] the data used.
\item[\code{combinations}] a character vector representing the combinations of 
variables.
\item[\code{count}] the frequencies of these combinations.
\item[\code{percent}] the percentage of these combinations.
\item[\code{missings}] a \code{data.frame} containing the amount of missing/imputed values 
in each variable.
\item[\code{tabcomb}] the indicator matrix for the combinations of variables.
\end{ldescription}
\end{Value}
%
\begin{Note}\relax
Some of the argument names and positions have changed with version 1.3 
due to extended functionality and for more consistency with other plot 
functions in \code{VIM}.  For back compatibility, the arguments 
\code{labs} and \code{names.arg} can still be supplied to \code{...} 
and are handled correctly.  Nevertheless, they are deprecated and no 
longer documented.  Use \code{ylabs} and \code{labels} instead.
\end{Note}
%
\begin{Author}\relax
Andreas Alfons, Matthias Templ, modifications by Bernd Prantner
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{print.aggr}{print.aggr}}, \code{\LinkA{summary.aggr}{summary.aggr}}
\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
data(sleep, package="VIM")
## for missing values
a <- aggr(sleep)
a
summary(a)

## for imputed values
sleep_IMPUTED <- kNN(sleep)
a <- aggr(sleep_IMPUTED, delimiter="_imp")
a
summary(a)
\end{ExampleCode}
\end{Examples}
