\HeaderA{colSequence}{HCL and RGB color sequences}{colSequence}
\aliasA{colSequenceHCL}{colSequence}{colSequenceHCL}
\aliasA{colSequenceRGB}{colSequence}{colSequenceRGB}
\keyword{color}{colSequence}
%
\begin{Description}\relax
Compute color sequences by linear interpolation based on a continuous color 
scheme between certain start and end colors.  Color sequences may thereby be 
computed in the \emph{HCL} or \emph{RGB} color space.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
colSequence(p, start, end, space = c("hcl", "rgb"), ...)

colSequenceHCL(p, start, end, gamma = 2.2, fixup = TRUE, ...)

colSequenceRGB(p, start, end, gamma = 2.2, fixup = TRUE, ...)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{p}] a numeric vector in \eqn{$[0,1]$}{} giving values to be used 
for interpolation between the start and end color (0 corresponds to the 
start color, 1 to the end color).
\item[\code{start, end}] the start and end color, respectively.  For HCL colors, 
each can be supplied as a vector of length three (hue, chroma, luminance) 
or an object of class "\code{\LinkA{polarLUV}{polarLUV}}".  For 
RGB colors, each can be supplied as a character string, a vector of length 
three (red, green, blue) or an object of class 
"\code{\LinkA{RGB}{RGB}}".
\item[\code{space}] character string; if \code{start} and \code{end} are both 
numeric, this determines whether they refer to HCL or RGB values.  Possible 
values are \code{"hcl"} (for the HCL space) or \code{"rgb"} (for the RGB 
space).
\item[\code{gamma}] numeric; the display \emph{gamma} value (see 
\code{\LinkA{hex}{hex}}).
\item[\code{fixup}] a logical indicating whether the colors should be corrected to 
valid RGB values (see \code{\LinkA{hex}{hex}}).
\item[\code{...}] for \code{colSequence}, additional arguments to be passed to 
\code{colSequenceHCL} or \code{colSequenceRGB}.  For \code{colSequenceHCL} 
and \code{colSequenceRGB}, additional arguments to be passed to 
\code{\LinkA{hex}{hex}}.
\end{ldescription}
\end{Arguments}
%
\begin{Value}
A character vector containing hexadecimal strings of the form 
\code{"\#RRGGBB"}.
\end{Value}
%
\begin{Author}\relax
Andreas Alfons
\end{Author}
%
\begin{References}\relax
Zeileis, A., Hornik, K., Murrell, P. (2009) Escaping RGBland: Selecting 
colors for statistical graphics. \emph{Computational Statistics \& Data 
Analysis}, \bold{53 (9)}, 1259--1270.
\end{References}
%
\begin{SeeAlso}\relax
\code{\LinkA{hex}{hex}}, \code{\LinkA{sequential\_hcl}{sequential.Rul.hcl}}
\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
p <- c(0, 0.3, 0.55, 0.8, 1)

## HCL colors
colSequence(p, c(0, 0, 100), c(0, 100, 50))
colSequence(p, polarLUV(L=90, C=30, H=90), c(0, 100, 50))

## RGB colors
colSequence(p, c(1, 1, 1), c(1, 0, 0), space="rgb")
colSequence(p, RGB(1, 1, 0), "red")
\end{ExampleCode}
\end{Examples}
