\HeaderA{marginmatrix}{Marginplot Matrix}{marginmatrix}
\aliasA{TKRmarginmatrix}{marginmatrix}{TKRmarginmatrix}
\keyword{hplot}{marginmatrix}
%
\begin{Description}\relax
Create a scatterplot matrix with information about missing/imputed values 
in the plot margins of each panel.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
marginmatrix(x, delimiter = NULL, col = c("skyblue","red","red4",
    "orange","orange4"), alpha = NULL, ...)

TKRmarginmatrix(x, delimiter = NULL, col = c("skyblue","red","red4",
    "orange","orange4"), alpha = NULL, ..., hscale = NULL,
    vscale = NULL, TKRpar = list())
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] a matrix or \code{data.frame}.
\item[\code{delimiter}] a character-vector to distinguish between variables
and imputation-indices for imputed variables (therefore, \code{x} needs
to have \code{\LinkA{colnames}{colnames}}). If given, it is used to determine the corresponding
imputation-index for any imputed variable (a logical-vector indicating
which values of the variable have been imputed). If such imputation-indices
are found, they are used for highlighting and the colors are adjusted 
according to the given colors for imputed variables (see \code{col}).
\item[\code{col}] a vector of length five giving the colors to be used in the 
marginplots in the off-diagonal panels.  The first color is used for 
the scatterplot and the boxplots for the available data, the second/fourth 
color for the univariate scatterplots and boxplots for the missing/imputed 
values in one variable, and the third/fifth color for the frequency of 
missing/imputed values in both variables (see `Details').  If only 
one color is supplied, it is used for the bivariate and univariate 
scatterplots and the boxplots for missing/imputed values in one variable, 
whereas the boxplots for the available data are transparent.  Else 
if two colors are supplied, the second one is recycled.
\item[\code{alpha}] a numeric value between 0 and 1 giving the level of 
transparency of the colors, or \code{NULL}.  This can be used to
prevent overplotting.
\item[\code{...}] further arguments and graphical parameters to be 
passed to \code{\LinkA{pairsVIM}{pairsVIM}} and \code{\LinkA{marginplot}{marginplot}}.  
\code{par("oma")} will be set appropriately unless supplied 
(see \code{\LinkA{par}{par}}).
\item[\code{hscale}] horizontal scale factor for plot to be embedded in a 
\emph{Tcl/Tk} window (see `Details').  The default value 
depends on the number of variables.
\item[\code{vscale}] vertical scale factor for the plot to be embedded in a 
\emph{Tcl/Tk} window (see `Details').  The default value 
depends on the number of variables.
\item[\code{TKRpar}] a list of graphical parameters to be set for the plot 
to be embedded in a \emph{Tcl/Tk} window (see `Details' and 
\code{\LinkA{par}{par}}).
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
\code{marginmatrix} uses \code{\LinkA{pairsVIM}{pairsVIM}} with a panel function 
based on \code{\LinkA{marginplot}{marginplot}}.

The graphical parameter \code{oma} will be set unless supplied as an 
argument.

\code{TKRmarginmatrix} behaves like \code{marginmatrix}, but uses 
\code{\LinkA{tkrplot}{tkrplot}} to embed the plot in a \emph{Tcl/Tk} 
window.  This is useful if the number of variables is large, because 
scrollbars allow to move from one part of the plot to another.
\end{Details}
%
\begin{Author}\relax
Andreas Alfons, modifications by Bernd Prantner
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{marginplot}{marginplot}}, \code{\LinkA{pairsVIM}{pairsVIM}}, 
\code{\LinkA{scattmatrixMiss}{scattmatrixMiss}}
\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
data(sleep, package = "VIM")
## for missing values
x <- sleep[, 1:5]
x[,c(1,2,4)] <- log10(x[,c(1,2,4)])
marginmatrix(x)

## for imputed values
x_imp <- kNN(sleep[, 1:5])
x_imp[,c(1,2,4)] <- log10(x_imp[,c(1,2,4)])
marginmatrix(x_imp, delimiter = "_imp")
\end{ExampleCode}
\end{Examples}
