\HeaderA{pairsVIM}{Scatterplot Matrices}{pairsVIM}
\keyword{hplot}{pairsVIM}
%
\begin{Description}\relax
Create a scatterplot matrix.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
pairsVIM(x, ..., delimiter = NULL, main = NULL, sub = NULL,
    panel = points, lower = panel, upper = panel, diagonal = NULL,
    labels = TRUE, pos.labels = NULL, cex.labels = NULL,
    font.labels = par("font"), layout = c("matrix","graph"), gap = 1)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] a matrix or \code{data.frame}.
\item[\code{delimiter}] a character-vector to distinguish between variables
and imputation-indices for imputed variables (therefore, \code{x} needs
to have \code{\LinkA{colnames}{colnames}}). If given, it is used to determine the corresponding
imputation-index for any imputed variable (a logical-vector indicating
which values of the variable have been imputed). If such imputation-indices
are found, they are used for highlighting and the colors are adjusted 
according to the given colors for imputed variables (see \code{col}).
\item[\code{main, sub}] main and sub title.
\item[\code{panel}] a \code{function(x, y, ...)}, which is used to plot
the contents of each off-diagonal panel of the display.
\item[\code{...}] further arguments and graphical parameters to be passed 
down.  \code{par("oma")} will be set appropriately unless supplied 
(see \code{\LinkA{par}{par}}).
\item[\code{lower, upper}] separate panel functions to be used below and above 
the diagonal, respectively.
\item[\code{diagonal}] optional \code{function(x, ...)} to be
applied on the diagonal panels.
\item[\code{labels}] either a logical indicating whether labels should be 
plotted in the diagonal panels, or a character vector giving 
the labels.
\item[\code{pos.labels}] the vertical position of the labels in the diagonal 
panels.
\item[\code{cex.labels}] the character expansion factor to be used for the 
labels.
\item[\code{font.labels}] the font to be used for the labels.
\item[\code{layout}] a character string giving the layout of the scatterplot 
matrix.  Possible values are \code{"matrix"} (a matrix-like layout 
with the first row on top) and \code{"graph"} (a graph-like layout 
with the first row at the bottom).
\item[\code{gap}] a numeric value giving the distance between the panels in 
margin lines.
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
This function is the workhorse for \code{\LinkA{marginmatrix}{marginmatrix}} and 
\code{\LinkA{scattmatrixMiss}{scattmatrixMiss}}.

The graphical parameter \code{oma} will be set unless supplied as an 
argument.

A panel function should not attempt to start a new plot, since the 
coordinate system for each panel is set up by \code{pairsVIM}.
\end{Details}
%
\begin{Note}\relax
The code is based on \code{\LinkA{pairs}{pairs}}.  Starting with version 
1.4, infinite values are no longer removed before passing the \code{x} and 
\code{y} vectors to the panel functions.
\end{Note}
%
\begin{Author}\relax
Andreas Alfons, modifications by Bernd Prantner
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{marginmatrix}{marginmatrix}}, \code{\LinkA{scattmatrixMiss}{scattmatrixMiss}}
\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
data(sleep, package = "VIM")
x <- sleep[, -(8:10)]
x[,c(1,2,4,6,7)] <- log10(x[,c(1,2,4,6,7)])
pairsVIM(x)
\end{ExampleCode}
\end{Examples}
