\HeaderA{pbox}{Parallel boxplots with information about missing/imputed values}{pbox}
\aliasA{TKRpbox}{pbox}{TKRpbox}
\keyword{hplot}{pbox}
%
\begin{Description}\relax
Boxplot of one variable of interest plus information about missing/imputed values 
in other variables.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
pbox(x, delimiter = NULL, pos = 1, selection = c("none","any","all"),
    col = c("skyblue","red","red4","orange","orange4"), numbers = TRUE, 
    cex.numbers = par("cex"), xlim = NULL, ylim = NULL, main = NULL,
    sub = NULL, xlab = NULL, ylab = NULL, axes = TRUE,
    frame.plot = axes, labels = axes, interactive = TRUE, ...)

TKRpbox(x, pos = 1, ..., delimiter = NULL, hscale = NULL, vscale = 1,
    TKRpar = list())
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x}] a vector, matrix or \code{data.frame}.
\item[\code{delimiter}] a character-vector to distinguish between variables
and imputation-indices for imputed variables (therefore, \code{x} needs
to have \code{\LinkA{colnames}{colnames}}). If given, it is used to determine the
corresponding imputation-index for any imputed variable (a logical-vector
indicating which values of the variable have been imputed). If such
imputation-indices are found, they are used for highlighting and the
colors are adjusted	according to the given colors for imputed variables
(see \code{col}).
\item[\code{pos}] a numeric value giving the index of the variable of 
interest.  Additional variables in \code{x} are used for 
grouping according to missingness/number of imputed missings.
\item[\code{selection}] the selection method for grouping according to 
missingness/number of imputed missings in multiple additional variables.
Possible values are \code{"none"} (grouping according to missingness/number
of imputed missings in every other variable that contains missing/imputed values),
\code{"any"} (grouping according to missingness/number of imputed missings in
\emph{any} of the additional variables) and \code{"all"} (grouping according to
missingness/number of imputed missings in \emph{all} of the additional variables).
\item[\code{col}] a vector of length five giving the colors to be used in the 
plot. The first color is used for the boxplots of the available data,
the second/fourth are used for missing/imputed data, respectively, 
and the third/fifth color for the frequencies of missing/imputed values
in both variables (see `Details').  
If only one color is supplied, it is used for the boxplots for missing/imputed 
data, whereas the boxplots for the available data are transparent.  
Else if two colors are supplied, the second one is recycled.
\item[\code{numbers}] a logical indicating whether the frequencies of missing/imputed 
values should be displayed (see `Details').
\item[\code{cex.numbers}] the character expansion factor to be used for the 
frequencies of the missing/imputed values.
\item[\code{xlim, ylim}] axis limits.
\item[\code{main, sub}] main and sub title.
\item[\code{xlab, ylab}] axis labels.
\item[\code{axes}] a logical indicating whether axes should be drawn 
on the plot.
\item[\code{frame.plot}] a logical indicating whether a box should be drawn 
around the plot.
\item[\code{labels}] either a logical indicating whether labels should be 
plotted below each box, or a character vector giving the labels.
\item[\code{interactive}] a logical indicating whether variables can be 
switched interactively (see `Details').
\item[\code{...}] for \code{pbox}, further arguments and graphical parameters 
to be passed to \code{\LinkA{boxplot}{boxplot}} and other functions.  
For \code{TKRpbox}, further arguments to be passed to \code{pbox}.
\item[\code{hscale}] horizontal scale factor for plot to be embedded in a 
\emph{Tcl/Tk} window (see `Details').  The default value 
depends on the number of boxes to be drawn.
\item[\code{vscale}] vertical scale factor for the plot to be embedded in a 
\emph{Tcl/Tk} window (see `Details').
\item[\code{TKRpar}] a list of graphical parameters to be set for the plot 
to be embedded in a \emph{Tcl/Tk} window (see `Details' and 
\code{\LinkA{par}{par}}).
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
This plot consists of several boxplots. First, a standard boxplot of the 
variable of interest is produced. Second, boxplots grouped by observed and 
missing/imputed values according to \code{selection} are produced for the variable 
of interest.

Additionally, the frequencies of the missing/imputed values can be represented 
by numbers.  If so, the first line corresponds to the observed values of 
the variable of interest and their distribution in the different groups, 
the second line to the missing/imputed values.

If \code{interactive=TRUE}, clicking in the left margin of the plot 
results in switching to the previous variable and clicking in the right 
margin results in switching to the next variable.  Clicking anywhere 
else on the graphics device quits the interactive session.

\code{TKRpbox} behaves like \code{pbox} with \code{selection="none"}, 
but uses \code{\LinkA{tkrplot}{tkrplot}} to embed the plot in a 
\emph{Tcl/Tk} window.  This is useful for drawing a large number of 
parallel boxes, because scrollbars allow to move from one part of the 
plot to another. 
\end{Details}
%
\begin{Value}
a list as returned by \code{\LinkA{boxplot}{boxplot}}.
\end{Value}
%
\begin{Note}\relax
Some of the argument names and positions have changed with version 1.3 
due to extended functionality and for more consistency with other plot 
functions in \code{VIM}.  For back compatibility, the arguments 
\code{names} and \code{cex.text} can still be supplied to \code{...} 
and are handled correctly.  Nevertheless, they are deprecated and no 
longer documented.  Use \code{labels} and \code{cex.numbers} instead.
\end{Note}
%
\begin{Author}\relax
Andreas Alfons, Matthias Templ, modifications by Bernd Prantner
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{parcoordMiss}{parcoordMiss}}
\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
data(chorizonDL, package = "VIM")
## for missing values
pbox(log(chorizonDL[, c(4,5,8,10,11,16:17,19,25,29,37,38,40)]))

## for imputed values
pbox(kNN(log(chorizonDL[, c(4,8,10,11,17,19,25,29,37,38,40)])),
    + delimiter = "_imp")
\end{ExampleCode}
\end{Examples}
