\HeaderA{rugNA}{Rug representation of missing/imputed values}{rugNA}
\keyword{color}{rugNA}
%
\begin{Description}\relax
Add a rug representation of missing/imputed values in only one of the variables to 
scatterplots.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
rugNA(x, y, ticksize = NULL, side = 1, col = "red", alpha = NULL,
    miss = NULL, lwd = 0.5, ...)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{x, y}] numeric vectors.
\item[\code{ticksize}] the length of the ticks.  Positive lengths give inward 
ticks.
\item[\code{side}] an integer giving the side of the plot to draw the rug 
representation.
\item[\code{col}] the color to be used for the ticks.
\item[\code{alpha}] the alpha value (between 0 and 1).
\item[\code{miss}] a \code{data.frame} or \code{matrix} with two columns and logical
values.	If \code{NULL}, \code{x} and \code{y} are searched for missing
values, otherwise, the first column of \code{miss} is used to determine the
imputed	values in \code{x} and the second one for the imputed values in
\code{y}.
\item[\code{lwd}] the line width to be used for the ticks.
\item[\code{...}] further arguments to be passed to 
\code{\LinkA{Axis}{Axis}}.
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
If \code{side} is 1 or 3, the rug representation consists of values 
available in \code{x} but missing/imputed in \code{y}.  Else if \code{side} 
is 2 or 4, it consists of values available in \code{y} but missing/imputed 
in \code{x}.
\end{Details}
%
\begin{Author}\relax
Andreas Alfons, modifications by Bernd Prantner
\end{Author}
%
\begin{Examples}
\begin{ExampleCode}
data(tao, package = "VIM")
## for missing values
x <- tao[, "Air.Temp"]
y <- tao[, "Humidity"]
plot(x, y)
rugNA(x, y, side = 1)
rugNA(x, y, side = 2)

## for imputed values
x_imp <- kNN(tao[, c("Air.Temp","Humidity")])
x <- x_imp[, "Air.Temp"]
y <- x_imp[, "Humidity"]
miss <- x_imp[, c("Air.Temp_imp","Humidity_imp")]
plot(x, y)
rugNA(x, y, side = 1, col = "orange", miss = miss)
rugNA(x, y, side = 2, col = "orange", miss = miss)
\end{ExampleCode}
\end{Examples}
